Assessment of zonally symmetric and asymmetric components of the Southern Annular Mode using a novel approach

### 2021-05-14 analysis/paper/asymsam.tex
Renderiza todo

\begin{figure}
\includegraphics{global-pp-1} \caption{Regression of annual and seasonal mean precipitation anomalies (mm per day, shading) with a) SAM, b) A\textbackslash nobreakdash-SAM and c) S\textbackslash nobreakdash-SAM for the 1979 -- 2018 period. Thin lines are the Black contours indicate areas with p-value smaller than 0.05 controlling for False Detection Rate. Note that the colour scale cuts-off at \(\pm0.25 \mathrm{K}\) so the areas of very high values in the Tropics don't wash out detail in the mid and high-latitudes.}\label{fig:global-pp}
\end{figure}

>>>>

\begin{figure}
\includegraphics{global-pp-1} \caption{Regression of annual and seasonal mean precipitation anomalies (mm per day, shading) with a) SAM, b) A\nobreakdash-SAM and c) S\nobreakdash-SAM for the 1979 -- 2018 period. Thin lines are the Black contours indicate areas with p-value smaller than 0.05 controlling for False Detection Rate. Note that the colour scale cuts-off at \(\pm0.25 \mathrm{K}\) so the areas of very high values in the Tropics don't wash out detail in the mid and high-latitudes.}\label{fig:global-pp}
\end{figure}
